Immutable Source-Mapped Abstract Syntax Tree:\ \\ A Design Pattern for Refactoring Engine APIs

### 2016-07-29 paper.tex
Moved preprocessor stuff to its own subsection.

Now, consider what happens when a user selects text in the text editor.  This
can be represented as an offset-length pair.  When source location information
is available for every AST node, it becomes fairly easy to determine what
syntactic construct corresponds to the text selection corresponds to: simply
walk the tree, searching for a node whose source location aligns with the
user's selection.

@@

%TODO work on this preprocessor stuff some more
%Maybe move to a different place?
Preprocessors (such as the C preprocessor and M4), don't interfere with the ASTs
used by compilers. In most cases, the preprocessing is performed first, and the
output thereof is used to construct the AST. The lexer/parser requires no 
knowledge of the fact that the text was preprocessed.

@@

%Preprocessors (such as the C preprocessor and M4) do not pose much of a problem
%for compilers.  In a compiler, the preprocessor can be run first, and then its
%output can serve as the input to the lexer/parser.  The preprocessor can be
%completely unaware of what lexer/parser it is feeding into, and the
%lexer/parser can be unaware of the fact that the code was preprocessed
%(although it might handle directives like \code{\#line} to give better error
%messages).
%
%Unfortunately, the C preprocessor makes refactoring very difficult; it is the
%subject of Garrido's entire Ph.D.~thesis~\cite{garrido05program}.  The
%compiler's approach of preprocesing the code first and then parsing it does not
%work.  Since refactoring tools must modify the \textit{user's} source code,
%they must be able to parse, analyze, and transform code \textit{with embedded
%preprocessor directives.}
%
%This dissertation will not treat the topic of refactoring preprocessed code in
%detail, but suffice it to say that a compiler's AST will almost certainly be
%inadequate.  At a minimum, a refactoring must be able to determine which AST
%nodes correspond to actual text in the user's source code and which ones are
%the result of file inclusions and macro expansions.  For more details, see
%Overbey et al.~\cite{wrt2009} and Garrido~\cite{garrido05program}.

%\subsection{Mapping AST Nodes to Source Locations}
%\label{ss:mapping}

>>>>

Now, consider what happens when a user selects text in the text editor.  This
can be represented as an offset-length pair.  When source location information
is available for every AST node, it becomes fairly easy to determine what
syntactic the text selection corresponds to: simply
walk the tree, searching for a node whose source location aligns with the
user's selection.

@@

%TODO work on this preprocessor stuff some more
%Maybe move to a different place?
\subsection{Preprocessors}
Preprocessors (such as the C preprocessor and M4), don't interfere with the ASTs
used by compilers. In most cases, the preprocessing is performed first, and the
output thereof is used to construct the AST. The lexer/parser requires no 
knowledge of the fact that the text was preprocessed.

@@
